Summary of PM2.5 Nonattainment  Analysis

### 2020-11-12 Analysis Files/Paper_Analysis_327.Rmd
1:1 matching
implemented for logistic reg propensity scores

>>>>

# NEW 1:k matching 
## 1:1 matching
NOTE: change propensity score method back to logistic before running this code for 1:1 matching
```{r}
# load required packages
library(DOS2); library(optmatch); library(RItools); library(plyr); library(rcbalance)
library(dplyr); library(tidyverse); library(gridExtra); library(sensitivitymult)
library(StatMatch)
source("utility.R") #helper functions for matching

# for ATTAINMENT (a=0) vs NON-ATTAINMENT (a=1)
## compute Mahalanobis distance matrix between treated and control for prop score
# rank-based Mahalanobis distance
mat.1 <- match_on(a ~ ps, data = dat)
mat.1 <- addcaliper(mat.1, z=dat$a, p=dat$ps, caliper=0.1)
# match on propensity score
ms.1 <- pairmatch(mat.1, data=dat) # matching method

# adat.1 <- summarize.match(dat, ms.1)

# plot(xBalance(a ~ PctMovedIn5 + MedianHValue + a_ozone + smokerate2000 + mean_age.2004 + Female_rate.2004 + White_rate.2004 + Black_rate.2004 + Tot_den_for_death_MA_FFS.2004 + avgdewpt + avgtemp + avgrelhum + logpop + CompletelyRural + pmbase + mortrate + CVDrate + resprate + avgtemp:avgrelhum + avgtemp:pmbase + strata(ms.1) -1, data=dat))

plot(xBalance(a ~ PctMovedIn5 + MedianHValue + a_ozone + smokerate2000 + mean_age.2004 + Female_rate.2004 + White_rate.2004 + Black_rate.2004 + Tot_den_for_death_MA_FFS.2004 + logpop + CompletelyRural + pmbase + mortrate + CVDrate + resprate + strata(ms.1) -1, data=dat))

# par(mar = c(5,10,2,2))
# bal.1 = mybalcheck(covariates=as.matrix(dat[, printvars, with = FALSE]), treatment=dat$a, propensity=dat$ps, strata=dat$pscat, absolute.es=FALSE, xlim=c(-1,2), outofrange=dat$outofrange, universal.psd=FALSE, plot.strata=FALSE, covnames = covnames)
```

```{r}
# summarize match function, modified for this data
ps.name="ps"
adat <- dat
adat$pair <- ms.1
adat <- adat[!is.na(adat$pair),]
adat.treat <- adat[adat$a==1, ]
adat.ctrl <- adat[adat$a==0, ]

adat.m <- as.data.frame(merge(adat.treat, adat.ctrl, by="pair", suffixes=c(".1", ".0")))
adat.m <- adat.m[, -which(names(adat.m) %in% c("a.1", "a.0", "pair"))]
adat.m <- adat.m[, sort(names(adat.m), index.return=TRUE)$ix]

p0.name <- paste0(ps.name,".", 0)
p1.name <- paste0(ps.name,".",1)

adat.m.tmp.1 <- adat.m[, -which(names(adat.m) %in% c(p0.name, p1.name))]
adat.m.tmp.2 <- adat.m[, c(p0.name, p1.name)]

adat.m <- cbind(adat.m.tmp.1, adat.m.tmp.2)
adat.1 <- adat.m

print(paste("Avg abs diff in propensity scores w/in matched pairs:",
            mean(abs(adat.1$ps.0-adat.1$ps.1))))

print(paste("Max abs diff in propensity scores w/in matched pairs:",
            max(abs(adat.1$ps.0-adat.1$ps.1))))
```
